### 2020-05-28 writeup/transfer.tex
fix

\textbf{Data size.}
In classical Rademacher or VC based theory of multi-task learning, adding more labeled data improves the generalization performance of a model.
On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
Using Example \ref{ex_basic}, we analyze the effect of varying the source task data size.

@@

\textbf{Improving Labeled Data Efficiency}
We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
This is formalized by a metric called the data efficiency ratio as follows.
Given several tasks, let $\alpha^{\star}$ be the largest factors such that the total number of labeled datapoints needed for solving all the tasks can be reduced by an $\alpha^{\star}$ factor (compared to training independently) while keeping the performance nearly the same.
More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
If we only use $\alpha n_i$ datapoints from every task to train the multi-task learning estimator $\hat{\beta}(\alpha)$, then $\alpha \in (0, 1)$ will be the smallest number such that
\[ \alpha^{\star} \define\argmin_{\alpha\in(0, 1)} ~~ \te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL}). \]
We quantify the data efficiency ratio of $\hat{\beta}_t^{\MTL}$ for Example \ref{ex_basic} as follows.

>>>>

\textbf{Data size.}
In classical Rademacher or VC based theory of multi-task learning, adding more labeled data improves the generalization performance of a model.
On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
Using the simplified model, we analyze the effect of varying the source task data size.

@@

\textbf{Improving Labeled Data Efficiency}
We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
This is formalized by a metric called the data efficiency ratio as follows.
Given several tasks, let $\alpha^{\star}$ be the largest factors such that the total number of labeled datapoints needed for solving all the tasks can be reduced by an $\alpha^{\star}$ factor (compared to training independently) while keeping the performance nearly the same.
More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
If we only use $\alpha n_i$ datapoints from every task to train the multi-task learning estimator $\hat{\beta}(\alpha)$, then $\alpha \in (0, 1)$ will be the smallest number such that
\[ \alpha^{\star} \define\argmin_{\alpha\in(0, 1)} ~~ \te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL}). \]
We quantify the data efficiency ratio of $\hat{\beta}_t^{\MTL}$ for the simplified model as follows.
